Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-22 cbm-rbd-paper.tex
system reliability calculation part done, small changes in policy part

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\def\Phinow{\Phi^{(t_\text{now})}}

@@

Following our comments at the end of Section~\ref{sec:weibull},
the component models can be further updated
using information gained from the current run of the system until $\tnow$:
Any failure times of failed components,
and the right-censoring time $\tpnow$ for each non-failed component
can be used to update $\nkz$ and $\ykz$.
We denote the resulting parameter values by $\nknow$ and $\yknow$.
%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
%must be used when calculating the posterior predictive distribution.

In analogue to the notation from Section~\ref{sec:weibull},
let $N_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
We can thus collect these observations, as of $\tnow$, in a vector
$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
containing $c_k^{\tnow}$ right-censored observations $\tpnow$.

$\Phinow$

@@

To find the optimal moment for maintenance based on the current set of system reliability curves,
we minimize the expected average cost per time unit,
called the unit cost rate, $g(\tau)$,
to find the cost-optimal moment of maintenance $\tau^*$
(could be discounted as well, out of scope here.)

In the literature, commonly two ways to calculate the unit cost rate are considered,
a renewal theory based long-term unit cost rate,
and the one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}.
Although the renewal theory based unit cost rate is often used
in CBM literature \citep{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation.
%since it considers only the costs with respect to the current cycle.

Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
As discussed in the Introduction,
we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$.

Conditional on the (random) system failure time $\Tsys$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsys) &=
\begin{cases}
c_p / \tau  & \text{if } \Tsys \ge \tau \\
c_u / \Tsys & \text{if } \Tsys < \tau
\end{cases}
\end{align*}

Taking the expectation over $\Tsys$ leads to the expected unit cost rate being
\begin{align}
g(\tau) &= \E[g(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
\label{eq:gtau}
\end{align}
***here, $\Rsys(\cdot)$ shifted such that $\tnow = 0$.

We approximate the integral in \eqref{eq:gtau} numerically by a sum,
where $\fsys(t)$ is calculated via differencen of $\Rsys(t)$ values on a dense grid.
$g(\tau)$ is likewise evaluated on a dense grid,
and $\tau^*_{\tnow} = \arg\min g(\tau)$ is determined as the minimum over the grid.
The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
$\tau^*$ depends on $\tnow$, and also on the history of the system.

At time $\tnow$, the corresponding $\tau^*_{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau^*_{\tnow}$.

****plot both $\tau^*_{\tnow}$ and $\tnow + \tau^*_{\tnow}$ over time for different failure histories

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}

@@

Following our comments at the end of Section~\ref{sec:weibull},
the component models can be further updated
using information gained from the current run of the system until $\tnow$:
Any failure times of failed components,
and the right-censoring time $\tpnow$ for each non-failed component
can be used to update $\nkz$ and $\ykz$ according to \eqref{eq:ig-update}.
We denote the resulting parameter values by $\nknow$ and $\yknow$.
%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
%must be used when calculating the posterior predictive distribution.

In analogue to the notation from Section~\ref{sec:weibull},
let $N_k = \eknow + \cknow$ be the number of type $k$ components in the monitored system,
where $\eknow$ is the number of components that have failed by $\tnow$,
and $\cknow$ is the number of components that have not failed by $\tnow$.
We can thus collect these observations, as of $\tnow$, in a vector
$\vectknow = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
containing $\cknow$ right-censored observations $\tpnow$.
%
The resulting posterior predictive distribution for any $t > \tnow$ is obtained as
\begin{align}
\lefteqn{%
P(C^k_t = l_k\mid\nkz,\ykz, \vectknow) }\hspace*{5.75ex} \nonumber\\  %
 &= { \cknow \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{3.5ex}
                               \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{\cknow - l_k}
    f(\lambda_k\mid\nkz,\ykz,\vectknow) \dd \lambda_k\,,
\label{eq:postpredtnow}
\end{align}
where $T^k$ is the Weibull distributed lifetime of a component of type $k$.
Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has
\begin{align}
P(T^k \leq t \mid T^k > \tnow, \lambda_k)
 &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
 &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
\label{eq:weibullcondprob}
\end{align}
Substituting \eqref{eq:weibullcondprob} and the posterior \eqref{eq:ig-update-alpha} using $\vectknow$,
written in terms of the updated parameters $\nknow$ and $\yknow$,
into \eqref{eq:postpredtnow}, we get
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)}\hspace*{5.75ex} \nonumber\\
 &= { \cknow \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
                               \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{\cknow - l_k}
    \times \nonumber\\ & \hspace*{14.5ex}
    \frac{\big(\nknow\yknow\big)^{\nknow + 1}}{\Gamma(\nknow + 1)}
    \lambda_k^{-(\nknow + 1) - 1} e^{-\frac{\nknow\yknow}{\lambda_k}} \dd \lambda_k \nonumber\\
 &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j}
    \frac{\big(\nknow\yknow\big)^{\nknow + 1}}{\Gamma(\nknow + 1)} 
    \times \nonumber\\ & \hspace*{1ex}
    \int \lambda_k^{-(\nknow + 1) - 1}
    \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nknow\yknow}{\lambda_k}\Big\} \dd \lambda_k\,.
\end{align}
The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
with parameters $\nknow + 1$ and $\nknow\yknow + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
allowing to solve the integral using the corresponding normalization constant.
We thus have, for $l_k \in \{0,1,\ldots,\cknow\}$,
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)} \nonumber\\
 &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j}
    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
 &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
 &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
    \nkz + \eknow + 1}.
\label{eq:postpred-priorparams}
\end{align}
%These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf)
%\begin{align}
%F(l_k \mid \nkz,\ykz,\vectknow) = P(C^k_t \leq l_k \mid \nkz,\ykz,\vectknow) 
% = \sum_{j=0}^{l_k} P(C^k_t = j \mid \nkz,\ykz,\vectknow)\,.
%\end{align}

\subsection{System reliability function at $\tnow$}

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system reliability distribution $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &:= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
                \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Note that if one or several components have failed by $\tnow$,
the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.

Next, we will describe how an adaptive maintenance policy based on \eqref{eq:sysrel-tnow}
can be obtained.

@@

To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
we minimize the expected average cost per time unit,
called the unit cost rate, $g(\tau)$,
to find the cost-optimal moment of maintenance $\tau_*$
(could be discounted as well, out of scope here.)

We use the expected one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
to calculate the unit cost rate.
Although a different, renewal theory based way to calculate the unit cost rate is often used
in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation,
where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$.
%since it considers only the costs with respect to the current cycle.

\subsection{Expected unit cycle cost rate}

Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$,
and these are exactly the situations where CBM is most effective (***cite working paper on relative benefit).

As discussed in the Introduction,
we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
That means that every time a new cycle starts, the system is the same state with all components (as-good-as) new.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
notation explodes to account for that***

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \Tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite.

$\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient (****)

***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

***if $\gnow(\tau)$ monotonely decreasing, corrective maintenance is optimal: policy switch!

\subsection{Numerical optimization of the expected unit cycle cost rate}

*** not possible / *** to minimize $\gnow(\tau)$ analytically.

We approximate the integral in \eqref{eq:gtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tau_*^{(\tnow)} = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

***calculations in \textsf{R} can be vectorized and are thus fast.

At time $\tnow$, the corresponding $\tau_*^{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.

***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy

****plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories

\subsection{Operational procedure}

*** could update $\tau_*$ every time a component fails,
but (near) real-time update of $\tau_*$ possible and useful as non-failed components still contribute to knowledge base via right-censored observation $\tpnow$.
